\hi{} and \ovi{} Emission from the Circum-Galactic Medium with a large sample of cosmological hydrodynamical simulations

### 2016-03-29 ms_oviemission.tex
28 Mar uncompleted draft

\def \etal {et~al.~}
\def \eg{e.g.}
\def \Section{\S}
\def \spose#1{\hbox  to 0pt{#1\hss}}  
\def \lta{\mathrel{\spose{\lower 3pt\hbox{$\sim$}}\raise  2.0pt\hbox{$<$}}}
\def \gta{\mathrel{\spose{\lower  3pt\hbox{$\sim$}}\raise 2.0pt\hbox{$>$}}}
\def \ion#1#2{#1{\footnotesize{#2}}\relax}
\def \ha       {H$\alpha$}
\def \hi       {\ion{H}{I}}
\def \hii      {\ion{H}{II}}
\def \oii      {[\ion{O}{II}]}

@@

\title[OVI Emssivity] {HI and OVI Emission from the Circum-Galactic Medium
 with a large sample of cosmological hydrodynamical simulations}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to study ultra-violet (UV)
  emission from circum-galactic medium (CGM) in galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses. We analyze the spatially-extended structures of emission lines
  from OVI and Ly$\alpha$.
\end{abstract}

@@

The hot and cold gas phases were indicated by OVI and HI ions in observation
commomly.

{\bf What can we gain from  HI and OVI in CGM}

\citet{Gutcke16} compared the column density profiles of OVI and HI
in CGM with observations.

{\bf What is the advantage of emssion line of HI and OVI}

\citet{Sravan15} studied ultra-violet (UV) metal line emission from the CGM
of high-redshift ($z=2-4$) galaxies using cosmological simulations from the 
Feedback in Realistic Environments (FIRE) project.

This paper is organized as follows: The cosmological hydrodynamical
simulations and the methodology for computing metal line emission
are briefly described in  \S\ref{sec:method}; In \S\ref{sec:results} 
we present the results including the Ly$\alpha$ and OVI emission map,
surface brightness and luminosity evolutions of all galaxies in NIHAO
sample; \S\ref{sec:sum} gives discussion and  summary of our
results.

@@

The simulations studied in this work are from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project \citep{Wang15}.  
The halos to be re-simulated with baryons have been extracted from 
3 different pure N-body simulations with a box size of 60, 20 and 
15 $h^{-1}$ Mpc respectively\citet{Dutton14}. 
All halos across the whole mass range with typically a million dark
matter particles inside the virial radius of the target halo at 
redshift $z=0$.  
We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.

@@

To compute the HI neutral fraction, like \citep{Gutcke16}, we used the 
self-shielding approximation presented in \citep{Rahmati13}.
{\bf say more detail about it}. Contrastly, To compute the OVI, the 
self-shielding approximation is not necessary to consider. {\bf reason}

@@

In order to estimate the evolution of total OVI and HI luminosities inside
$2 \Rvir$, we employ the grids 
of emissivities computed since z=4 to present to evaluate the evolution of 
luminosities of all galaxies in NIHAO sample from particle data directly.
The method is similar to the one used by \citep{Sravan15}, the OVI and HI 
luminosities of each gas particle are calculated as
\begin{equation}
L = \epsilon_{\odot}\left(z,n_H,T\right)\left(\frac{m_{gas}}{\rho_{gas}}\right)
    \left(\frac{Z_{gas}}{Z_{\odot}}\right),
\end{equation}
where $m_{gas}$, $\rho_{gas}$ and $Z_{gas}$ are the mass, density and 
metallicity of the gas particle, and $\epsilon_{\odot}\left(z,n_H,T\right)$
is the emissivity interpolated bi-linearly from pre-computed grids of 
emissivities with given redshift, hydrogen number density and temperature.

@@

\subsection{OVI and HI Emissivity Maps and Radial Profile}
\label{sec:map_rp}

>>>>

\def \etal {et~al.~}
\def \eg{e.g.}
\def \Section{\S}
\def \spose#1{\hbox  to 0pt{#1\hss}}  
\def \lta{\mathrel{\spose{\lower 3pt\hbox{$\sim$}}\raise  2.0pt\hbox{$<$}}}
\def \gta{\mathrel{\spose{\lower  3pt\hbox{$\sim$}}\raise 2.0pt\hbox{$>$}}}
\def \ion#1#2{#1{\footnotesize{#2}}\relax}
\def \ha       {H$\alpha$}
\def \hi       {\ion{H}{I}}
\def \hii      {\ion{H}{II}}
\def \oii      {[\ion{O}{II}]}
\def \ovi      {\ion{O}{VI}}

@@

\title[\hi{} and \ovi{} Emssivity] {\hi{} and \ovi{} Emission from the Circum-Galactic Medium
 with a large sample of cosmological hydrodynamical simulations}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to study ultra-violet (UV)
  emission from circum-galactic medium (CGM) in galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses. We analyze the spatially-extended structures of emission lines
  from \ovi{} and \hi{}.
\end{abstract}

@@

The hot and cold gas phases were indicated by \ovi{} and \hi{} ions in observation
commomly.

{\bf What can we gain from  \hi{} and \ovi{} in CGM}

\citet{Gutcke16} compared the column density profiles of \ovi{} and \hi{}
in CGM of galaxies of the cosmologycal hydrodynamical simulation suite 
NIHAO \citep{Wang15} with observations, studied the covering fraction of 
dense \hi{}, looked at the shape of the CGM and its chemical composition.
The simulations have a good agreement with observations and show observers
and modellers can compare with them in future studies.

However, the works mentioned above all relate to the absorption lines of
\hi{} and \ovi{}, there are rare simulations comparing the emission lines
of them with observations.
{\bf What is the advantage of emssion line of \hi{} and \ovi{}}

\citet{Sravan15} studied ultra-violet (UV) metal line emission from the CGM
of high-redshift ($z=2-4$) galaxies using cosmological simulations from the 
Feedback in Realistic Environments (FIRE) project.
For each simulation, they predicted the emission from multiple metal lines
including \hi{} and \ovi{}, and found more massive haloes are on average 
more UV-luminous and the UV metal line emission is primarily from collisionally
ionized gas and strongly time variable. The high UV-luminous event correspond
high star formation and \ion{C}{III}, \ion{Si}{III}, \ion{C}{IV} and \ion{Si}{IV}
should be detectable by current and upcoming intergral field spectrographs such
as the Multi Unit Spectroscopic Explorer (MUSE{\bf citation}).

In this paper we investigate the CGM \ovi{} and \hi{} emissivity distribution
and shape in Numerical Investigation of a Hundred Astrophysical Objects,
NIHAO \citep{Wang15} project.
NIHAO project produced nearly 100 hydrodynamical, cosmological zoom-in galaxies
across a range in mass from

This paper is organized as follows: The cosmological hydrodynamical
simulations and the methodology for computing metal line emission
are briefly described in  \S\ref{sec:method}; In \S\ref{sec:results} 
we present the results including the \hi{} and \ovi{} emission map,
surface brightness and luminosity evolutions of all galaxies in NIHAO
sample; \S\ref{sec:sum} gives discussion and  summary of our
results.

@@

The simulations studied in this work are from the NIHAO project \citep{Wang15}.  
The halos to be re-simulated with baryons have been extracted from 
3 different pure N-body simulations with a box size of 60, 20 and 
15 $h^{-1}$ Mpc respectively\citet{Dutton14}. 
All halos across the whole mass range with typically a million dark
matter particles inside the virial radius of the target halo at 
redshift $z=0$.  
We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.

@@

To compute the \hi{} neutral fraction, like \citep{Gutcke16}, we used the 
self-shielding approximation presented in \citep{Rahmati13}.
{\bf say more detail about it}. Contrastly, To compute the \ovi{}, the 
self-shielding approximation is not necessary to consider. {\bf reason}

@@

In order to estimate the evolution of total \ovi{} and \hi{} luminosities inside
$2 \Rvir$, we employ the grids 
of emissivities computed since z=4 to present to evaluate the evolution of 
luminosities of all galaxies in NIHAO sample from particle data directly.
The method is similar to the one used by \citep{Sravan15}, the \ovi{} and \hi{} 
luminosities of each gas particle are calculated as
\begin{equation}
L = \epsilon_{\odot}\left(z,n_H,T\right)\left(\frac{m_{gas}}{\rho_{gas}}\right)
    \left(\frac{Z_{gas}}{Z_{\odot}}\right),
\end{equation}
where $m_{gas}$, $\rho_{gas}$ and $Z_{gas}$ are the mass, density and 
metallicity of the gas particle, and $\epsilon_{\odot}\left(z,n_H,T\right)$
is the emissivity interpolated bi-linearly from pre-computed grids of 
emissivities with given redshift, hydrogen number density and temperature.

@@

\subsection{\protect\ovi{} and \protect\hi{} Emissivity Maps and Radial Profile}
\label{sec:map_rp}
